Supplementary material for ``Current status and prospects of R-packages for the design of experiments''

### 2022-06-15 supp.Rmd
update renv + supp

---
title: Supplmentary material for "Current status and prospects of R-packages for the design of experiments"
author:
  - Emi Tanaka
  - Dewi Amaliah 
bibliography: pkgs.bib
keywords: ["experimental design", "CRAN task view", "user interface"]
output: 
  bookdown::pdf_document2:
    toc: false
    keep_tex: true
    citation_package: biblatex
header-includes: |
  \usepackage{colortbl}
  \usepackage{bera}
  \usepackage{xcolor}
  \usepackage{hyperref}
  \usepackage{booktabs}
  \usepackage[utf8]{inputenc}
  \usepackage{caption}
  \renewcommand{\figurename}{Figure S}
  \makeatletter
  \def\fnum@figure{\figurename\thefigure}
  \makeatother
  \renewcommand{\tablename}{Table S}
  \makeatletter
  \def\fnum@table{\tablename\thetable}
  \makeatother

@@

```{r setup, cache = FALSE, include = FALSE}
library(targets)
library(glue)
library(tidyverse)
library(patchwork)
library(tidygraph)
library(ggraph)
source("R/plot.R")
knitr::opts_chunk$set(echo = FALSE, 
                      cache = TRUE,
                      cache.path = "cache/",
                      fig.align = 'center', 
                      fig.pos = 'htbp', 
                      fig.path = "figures/",
                      fig.width = 6,
                      fig.height = 6.5,
                      message = FALSE,
                      warning = FALSE)

@@

tar_load(npkgs)
tar_load(gini_yearly)
tar_load(gini_yearly_ctv)

#renvLock <- jsonlite::read_json("renv.lock")
#sink("pkgs.bib")
#knitr::write_bib(names(renvLock$Packages))
#sink()
```

@@

```{r session-info, echo = FALSE}
renv_lock <- jsonlite::read_json("renv.lock")
pander::pander(sessionInfo(package = names(renv_lock$Packages)), compact = FALSE)
```

>>>>

---
title: Supplementary material for "Current status and prospects of R-packages for the design of experiments"
author:
  - Emi Tanaka
  - Dewi Amaliah 
bibliography: pkgs.bib
keywords: ["experimental design", "CRAN task view", "user interface"]
output: 
  bookdown::pdf_document2:
    toc: false
    keep_tex: true
    citation_package: biblatex
header-includes: |
  \usepackage{colortbl}
  \usepackage{bera}
  \usepackage{xcolor}
  \usepackage{hyperref}
  \usepackage{booktabs}
  \usepackage[utf8]{inputenc}
  \usepackage{caption}
  \renewcommand{\figurename}{Figure S}
  \makeatletter
  \def\fnum@figure{\figurename\thefigure}
  \makeatother
  \renewcommand{\tablename}{Table S}
  \makeatletter
  \def\fnum@table{\tablename\thetable}
  \makeatother

@@

```{r setup, cache = FALSE, include = FALSE}
library(targets)
library(glue)
library(tidyverse)
library(patchwork)
library(tidygraph)
library(ggraph)
library(pander)
source("R/plot.R")
knitr::opts_chunk$set(echo = FALSE, 
                      cache = TRUE,
                      cache.path = "cache/",
                      fig.align = 'center', 
                      fig.pos = 'htbp', 
                      fig.path = "figures/",
                      fig.width = 6,
                      fig.height = 6.5,
                      message = FALSE,
                      warning = FALSE)

@@

tar_load(npkgs)
tar_load(gini_yearly)
tar_load(gini_yearly_ctv)
```

@@

```{r session-info, echo = FALSE}

renv_lock <- jsonlite::read_json("renv.lock")
pkgs <- intersect(setdiff(names(renv_lock$Packages), "cranscrub"),
                  rownames(available.packages(repos = "https://cran.rstudio.com/")))
pander::pander(sessionInfo(package = pkgs), compact = FALSE)
```

### 2022-06-15 supp.tex
update renv + supp

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplmentary material for ``Current status and prospects of R-packages for the design of experiments''},
  pdfauthor={Emi Tanaka; Dewi Amaliah},
  pdfkeywords={experimental design, CRAN task view, user interface},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{colortbl}
\usepackage{bera}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\renewcommand{\figurename}{Figure S}
\makeatletter
\def\fnum@figure{\figurename\thefigure}
\makeatother
\renewcommand{\tablename}{Table S}
\makeatletter
\def\fnum@table{\tablename\thetable}
\makeatother

@@

\title{Supplmentary material for ``Current status and prospects of R-packages for the design of experiments''}
\author{Emi Tanaka \and Dewi Amaliah}
\date{}

@@

!6\}\{ModelDeployment\} \& \cellcolor{gray!6}{Model Deployment with R} \& \cellcolor{gray!6}{31} \& \cellcolor{gray!6}{146} \& \cellcolor{gray!6}{6.55} \& \cellcolor{gray!6}{74}\textbackslash*
\textbackslash end\{longtable\}

@@

  MASS(v.7.3-57)

@@

  Matrix(v.1.4-1)

@@

  RColorBrewer(v.1.1-3)

@@

  Rcpp(v.1.0.8.3)

@@

@@

  colorspace(v.2.0-3)

@@

  cranscrub(v.0.0.0.9000)
  crayon(v.1.5.1)

@@

  fansi(v.1.0.3)

@@

  ggplot2(v.3.3.6)

@@

  glue(v.1.6.2)

@@

  httr(v.1.4.3)

@@

  igraph(v.1.3.1)

@@

  jsonlite(v.1.8.0)

@@

  magrittr(v.2.0.3)

@@

  mgcv(v.1.8-40)

@@

  nlme(v.3.1-157)

@@

@@

@@

  scales(v.1.2.0)

@@

  tibble(v.3.1.7)

@@

  withr(v.2.5.0)

@@

  yaml(v.2.3.5)

@@

\begin{itemize}
\tightlist
\item
  utils(v.4.1.2)
\item
  DiceDesign(v.1.9)
\item
  tools(v.4.1.2)
\item
  compiler(v.4.1.2)
\item
  datasets(v.4.1.2)
\item
  base(v.4.1.2)
\item
  grDevices(v.4.1.2)
\item
  grid(v.4.1.2)
\item
  methods(v.4.1.2)
\item
  pander(v.0.6.5)
\item
  graphics(v.4.1.2)
\item
  BsMD(v.2020.4.30)
\item
  stats(v.4.1.2)
\item
  rsm(v.2.10.3)
\end{itemize}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary material for ``Current status and prospects of R-packages for the design of experiments''},
  pdfauthor={Emi Tanaka; Dewi Amaliah},
  pdfkeywords={experimental design, CRAN task view, user interface},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{colortbl}
\usepackage{bera}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\renewcommand{\figurename}{Figure S}
\makeatletter
\def\fnum@figure{\figurename\thefigure}
\makeatother
\renewcommand{\tablename}{Table S}
\makeatletter
\def\fnum@table{\tablename\thetable}
\makeatother

@@

\title{Supplementary material for ``Current status and prospects of R-packages for the design of experiments''}
\author{Emi Tanaka \and Dewi Amaliah}
\date{}

@@

@@

  MASS(v.7.3-54)

@@

  Matrix(v.1.3-4)

@@

  RColorBrewer(v.1.1-2)

@@

  Rcpp(v.1.0.8)

@@

  coda(v.0.19-4)

@@

  colorspace(v.2.0-2)

@@

  crayon(v.1.4.2)

@@

  fansi(v.1.0.2)

@@

  ggplot2(v.3.3.5)

@@

  glue(v.1.6.1)

@@

  httr(v.1.4.2)

@@

  igraph(v.1.2.11)

@@

  jsonlite(v.1.7.3)

@@

  magrittr(v.2.0.2)

@@

  mgcv(v.1.8-38)

@@

  nlme(v.3.1-153)

@@

  pander(v.0.6.6)

@@

  remotes(v.2.4.2)

@@

  scales(v.1.1.1)

@@

  tibble(v.3.1.6)

@@

  withr(v.2.4.3)

@@

  yaml(v.2.2.2)

@@

\begin{itemize}
\tightlist
\item
  utils(v.4.1.2)
\item
  tools(v.4.1.2)
\item
  compiler(v.4.1.2)
\item
  datasets(v.4.1.2)
\item
  base(v.4.1.2)
\item
  grDevices(v.4.1.2)
\item
  grid(v.4.1.2)
\item
  methods(v.4.1.2)
\item
  graphics(v.4.1.2)
\item
  stats(v.4.1.2)
\end{itemize}
